Icicle: write once, run once

### 2016-06-07 2016fhpc/section/01-Introduction.tex
More edits to intro

\item
We present production benchmarks of Icicle compiled code which outperforms an existing R feature generation system by several orders of magnitude, and are on par with standard Unix utilities that conceptually perform less work\sref{s:Benchmarks}.
\end{itemize}

>>>>

\item
We present production benchmarks of Icicle compiled code which outperforms an existing R feature generation system by several orders of magnitude\sref{s:Benchmarks}. 
\end{itemize}

% , and are on par with standard Unix utilities.
% that conceptually perform less work.
%\ben{I think this clause confuses the contribution. If if Icicle is "on par" with standard unix utilities, then why not just use those standard utilities? The point is that with Icicle we can also fuse multiple queries, and the fused code should be at least as good as the unix utils. However, fusing two instances of 'wc' won't be exactly 2x fast then running them sequentially, but still better than actually running them sequentially. There's no space to discuss the details in the intro.
